---
title: "Analysis of Behaviour using DeepLabCut and R"
author: "Hung Lo & Daniel Parthier"
date: "27.08.2020"
output:
  ioslides_presentation:
    transition: slower
    widescreen: true
    smaller: false
    incremental: true
    logo: logo_schmitzlab_black.png
    css: styles.css
bibliography: "BehaviourAnalysis.bib"
keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(DiagrammeR)
```

## Motivation
* Use full potential of video data
  + Time resolution
  + Spatial information
  + Have control over parameter estimation
  + Easy integration in analysis workflow

## DeepLabCut
* Machine learning implementation by **@mathis_deeplabcut_2018**
  + Written in `Python` and based on *TensorFlow* **[@martin_abadi_tensorflow_2015]**
  + can run on *CPU*, *GPU*, or *TPU*
  + Computation can be outsourced (*Google Colab*)
* Easy training of model
  + GUI implementation
* Fast extraction of feature coordinates
* High resolution and accuracy (different body parts)
  
## Running DeepLabCut {.build}
* On local machine
```{bash, echo=T, eval=F}
conda env create -f DLC-CPU.yaml    # run on CPU
conda env create -f DLC-GPU.yaml    # run on GPU
```
* Future version of `BehaviouR` could include function call from within `R`

* Run in the cloud!
    + *Google Colab* demonstration by Hung

## R Package (`BehaviouR`)
* Package using the *DeepLabCut* output
* Features
    + Smoothing of tracking
    + Grouping of labels
    + Helper functions (distance, speed, angles, centroids, plotting, etc.)
    + Stationary object functions
    + Batch analysis
    + GUI implementation as `shiny`-app
    + Multithreading (powered by `DataTable`)
  
## Data Structure {.build}
* Nested `DataTable`
    + `CoordTable` and `ObjectTable`
```{r, echo=TRUE, eval=F, fig.cap="Function to load data"}
# Load data from DeepLabCut
MouseBodyList <- list()
MouseBodyList$head <- c("ear", "nose")
MouseBodyList$body <- c("ear", "tail")
ObjectList <- list("object")
BehaviouR::DeepLabCutLoad(FileName = "DeepLabCut_ouput.csv",
                          FrameRate = 30,
                          MouseLabels = MouseBodyList,
                          ObjectLabels = ObjectList,
                          JumpCorrections = T,
                          includeAll = F)
```

## Workflow
```{r echo=FALSE}
grViz("digraph Workflow {
      # node definitions with substituted label text
      node [fontname = Helvetica, shape = rectangle]        
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']
      tab6 [label = '@@6']
      tab7 [label = '@@7']
      tab8 [label = '@@8']

      # edge definitions with the node IDs
      tab1 -> tab2 -> tab3 -> tab4 -> tab5;
      tab4 -> tab6
      tab5 -> tab7
      tab8 -> tab5
      tab3 -> tab6
      tab6 -> tab8
      }

      [1]: 'Video of Experiment'
      [2]: 'Extraction of Feature Coordinates (DeepLabCut)'
      [3]: 'Postprocessing (BehaviouR)'
      [4]: 'Calculation of Parameters (BehaviouR, DataTable etc.)'
      [5]: 'Statistical Analysis (lme4, brms, etc.)'
      [6]: 'Export Data as csv etc.'
      [7]: 'Report Summary'
      [8]: 'External Calculation of Parameters (Python, MATLAB, etc.)'
      ", width = 1000)
```

## References


